Asteroid project summary

### 2022-02-01 summaries/21-11/21-11.tex
Staged gap for 3 hours

\begin{itemize}
\item Asteroids simulated in binaries \cite{Naidu_2015}
\item Previous work on the math of asteroid rotations \cite{ashenberg07, paul88}
\item CNEOS: 4 asteroids $D > 100 m$ are coming to within 1 LD of Earth in the next 10 years, 29 with $D > 10 m$.
\item Moskowitz survey of Duende: \cite{BENSON2020113518} with companion observational article \cite{MOSKOVITZ2020113519}. Demonstrates that moment of inertia can be extracted from a tumbling asteroid via lightcurve analysis in the zero-torque regime (fourier transform of lightcurve to pick up on two frequencies and assign precession and nutation frequencies to them.) Assumes constant geometry.
\item Study of asteroid binary to extract density \cite{DESCAMPS2020113726}
\item Scheeres theoretical paper \cite{HouMar2017} detailing the different forces and torques felt by an asteroid.
\item Paper stating in general that asteroids can be tidally disrupted on hyperbolic flyby. \cite{SCHEERES2000106}, plus similar paper \cite{RICHARDSON199847} for tidal disruption
\item Another theoretical paper \cite{BOUE2009750} inspired by Paul
\item Apophis will definitely pass by Earth and will definitely significantly change its rotation state, but will not undergo tidal disruption. \cite{SCHEERES2005281}
\end{itemize}

@@

We represent 1-$\sigma$ uncertainty in the fit parameters as the difference between the 84th or 15th percentile of the marginal posterior PDF for each fit parameter and its mean. For a multivariate gaussian posterior PDF (which must also have gaussian marginal PDFs), this 1-$\sigma$ uncertainty is exactly the standard deviation of the marginal PDF. We perform a similar exercise for the 2-$\sigma$ uncertainty.

@@

>>>>

\begin{itemize}
\item Asteroids simulated in binaries \cite{Naidu_2015}
\item Previous work on the math of asteroid rotations \cite{ashenberg07, paul88}
\item CNEOS: 4 asteroids $D > 100 m$ are coming to within 1 LD of Earth in the next 10 years, 29 with $D > 10 m$.
\item Moskowitz survey of Duende: \cite{BENSON2020113518} with companion observational article \cite{MOSKOVITZ2020113519}. Demonstrates that moment of inertia can be extracted from a tumbling asteroid via lightcurve analysis in the zero-torque regime (Fourier transform of lightcurve to pick up on two frequencies and assign precession and nutation frequencies to them.) Assumes constant geometry.
\item Study of asteroid binary to extract density \cite{DESCAMPS2020113726}
\item Scheeres theoretical paper \cite{HouMar2017} detailing the different forces and torques felt by an asteroid.
\item Paper stating in general that asteroids can be tidally disrupted on hyperbolic flyby. \cite{SCHEERES2000106}, plus similar paper \cite{RICHARDSON199847} for tidal disruption
\item Another theoretical paper \cite{BOUE2009750} inspired by Paul
\item Apophis will definitely pass by Earth and will definitely significantly change its rotation state, but will not undergo tidal disruption. \cite{SCHEERES2005281}
\end{itemize}

@@

We represent 1-$\sigma$ uncertainty in the fit parameters as the difference between the 84th or 15th percentile of the marginal posterior PDF for each fit parameter and its mean. For a multivariate Gaussian posterior PDF (which must also have Gaussian marginal PDFs), this 1-$\sigma$ uncertainty is exactly the standard deviation of the marginal PDF. We perform a similar exercise for the 2-$\sigma$ uncertainty.

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{observation-gap.pdf}
  \caption{Observation gap}
  \label{fig:observation-gap}
\end{figure}
